\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[linesnumbered,lined]{algorithm2e}
\usepackage{scrextend}
\makeatletter
\renewcommand{\@algocf@capt@plain}{above}% formerly {bottom}
\makeatother
\usepackage{enumitem}
\setlist[enumerate]{listparindent=\parindent}
\usepackage{cleveref}%[nameinlink]
\crefname{lemma}{Lemma}{Lemmas}
\crefname{proposition}{Proposition}{Propositions}
\crefname{definition}{Definition}{Definitions}
\crefname{theorem}{Theorem}{Theorems}
\crefname{conjecture}{Conjecture}{Conjectures}
\crefname{corollary}{Corollary}{Corollaries}
\crefname{section}{Section}{Sections}
\crefname{appendix}{Appendix}{Appendices}
\crefname{figure}{Fig.}{Figs.}
\crefname{equation}{Eq.}{Eqs.}
\crefname{table}{Table}{Tables}
\crefname{algocf}{Algorithm}{Algorithms}

\title{Problem Set 0 - Solutions}
\author{}
\date{}

\parindent=.25in

\parskip 7.2pt 

\begin{document}
\maketitle

Please read the sections of the syllabus on problem sets and honor code before starting this homework.


\begin{enumerate}
\item  \textbf{[8 points]} Prove that for every odd integer $n$, $n^2-1$ is divisible by 8. 

\end{enumerate}

{\paragraph{Solution} Let $n$ be an odd integer. Then we can write $n=2k+1$, where $k\in \mathbb{Z}.$ Then
\begin{align}
n^2-1=(2k+1)^2-1=4k^2+4k=4(k^2+k).
\end{align}
Note that if $k^2+k$ is even, then $n^2-1$ is divisible by $8$, and we have our result.

We conider two cases: $k$ is even, or $k$ is odd. If $k$ is even, then $k^2$ is even, and so $k^2+k$ is even, because the sum of two even numbers is another even number. If $k$ is odd, then $k^2$ is odd, and so $k^2+k$ is odd, because the sum of two odd numbers is an even number.

Therefore, in either case, $k^2+k$ is even, so $4(k^2+k)$, and hence $n^2-1$, is divisible by $8.$ for every odd integer $n$.}

\end{document}