\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage[colorlinks]{hyperref}
\usepackage{url}\urlstyle{same}
\usepackage[T1]{fontenc}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}

\begin{document}

% ~\vspace{-4em}
% \hrule\hrule\smallskip\centerline{\Huge{\bf DRAFT}}\smallskip\hrule\hrule
% \bigskip



\hfill Name: $\underline{\textrm{Alice Exception}}$\newline
\noindent{\Large {Reflection Worksheet  }}\hfill Problem Set: $0$



\vspace{1cm}

Please write a paragraph reflecting on the learning process while both working on and grading this problem set. For example, what skills did the problem set help you to improve? are there are skills related to the problem set where you still need more practice? what concepts do you now understand, or don't yet understand? did you realize any misconceptions or repeated mistakes? what emotions did the problem set evoke (for example pride, frustration, confidence, confusion) and why?

\vspace{1cm}

\textit{When I was solving the problem set, I really thought I understood how to do the proof, so I was surprised when the solution was so different from what I wrote. I think the key thing that I was doing wrong was that I showed the statement was true only for a couple of values of n, but I didn't show it was true for all n. I'm a little nervous that even though now I know what is wrong with my old proof, I won't be able to create a good proof. I'm going to practice more to see if I can do something similar to the posted solutions on my own.}

\vspace{5cm}
\noindent Total Problem Set Points: $\underline{4/11}$ 

\end{document}